# Testing

This is just an area for me to test out a few things to help create this book. 

For instance, 

## Flowchart



Some stuff here.

```{r, echo=FALSE, engine='tikz', out.width='90%', fig.ext=if (knitr:::is_latex_output()) 'pdf' else 'png', fig.cap='Some caption.'}
\begin{tikzpicture}[scale=.7]
\draw [fill=gray!30,very thick] (0,-1) rectangle (5,1);
\draw [very thick] (5, 0) -- (13,0);
\node [below] at (2,-1) {\large Hello};
\node [below, align=center] at (0,-1) {\large Two\\ lines};
\end{tikzpicture}
```

```{r, echo=F}
library(DiagrammeR)
grViz("
digraph blorts {
      
node [fontname = Helvetica]

input     [label = 'Input Fastq', shape=oval, color=red, alpha=0.5, style=filled]
fastqc    [label = 'FastQC', shape=square]
multi     [label = 'MultiQC', shape=square]
qual      [label = 'Quality\nOverview', shape=oval]
ref       [label = 'Reference\nTranscriptome', shape=oval]
salmon    [label = 'Salmon', shape=square]
quant     [label = 'Quantification Files\n(quant.sf)', shape=oval]
deseq     [label = 'DESeq2', shape=square]
dds       [label = 'dds.Rds', shape=oval]
diff      [label = 'Differential Expression', shape=oval, color=green, style=filled]


input -> fastqc
fastqc -> multi
multi -> qual
fastqc -> salmon
ref -> salmon
salmon -> quant
quant -> deseq
deseq -> dds
deseq -> diff


}      ")


```

\begin{equation}
	\sum x_{i}
\end{equation}

```{r, echo=FALSE, warning=FALSE,message=FALSE,error=FALSE}
library(diagram)
 
# creates an empty plot
openplotmat()
 
library(diagram)

#par(mar = c(1, 1, 1, 1))
#openplotmat(main = "RNA seq")

plot.new( )
plot.window( xlim=c(-5,5), ylim=c(-5,5) )
boxX <- 0.1
boxY <- 0.05

pos <- coordinates (c(1, 5, 2,1, 1, 1, 3, 3, 3), mx = 10, my = -10)
#plot(pos, type='n')
#text(pos)

straightarrow(from = pos[1, ], to = pos[4, ], arr.type='simple')

straightarrow(from = pos[4, ], to = pos[3, ], arr.type='simple')
straightarrow(from = pos[3, ], to = pos[2, ], arr.type='simple')
straightarrow(from = pos[4, ], to = pos[9, ], arr.type='simple')
straightarrow(from = pos[8, ], to = pos[9, ], arr.type='simple')
straightarrow(from = pos[9, ], to = pos[10, ], arr.type='simple')
straightarrow(from = pos[10, ], to = pos[11, ], arr.type='simple')

straightarrow(from = pos[11, ], to = pos[12, ], arr.type='simple')
straightarrow(from = pos[11, ], to = pos[13, ], arr.type='simple')
straightarrow(from = pos[11, ], to = pos[14, ], arr.type='simple')

straightarrow(from = pos[12, ], to = pos[15, ], arr.type='simple')
straightarrow(from = pos[12, ], to = pos[16, ], arr.type='simple')
straightarrow(from = pos[12, ], to = pos[17, ], arr.type='simple')

straightarrow(from = pos[15, ], to = pos[18, ], arr.type='simple')
straightarrow(from = pos[16, ], to = pos[19, ], arr.type='simple')
straightarrow(from = pos[17, ], to = pos[20, ], arr.type='simple')

textellipse(pos[1,], radx=boxX, rady=boxY, lab='Input Reads\nfastq', box.col = 'red')



```



```
#```{r, echo=FALSE, engine='tikz', out.width='90%', fig.ext=if (knitr:::is_latex_output()) 'pdf' else 'png', fig.cap='Some caption.'}
\begin{document}

\begin{tikzpicture}[node distance=2cm]

\node (start) [startstop] {Start};
\node (in1) [io, below of=start] {Input};
\node (pro1) [process, below of=in1] {Process 1};
\node (dec1) [decision, below of=pro1, yshift=-0.5cm] {Decision 1};
\node (pro2a) [process, below of=dec1, yshift=-0.5cm] {Process 2a text text text text text text text text text text};
\node (pro2b) [process, right of=dec1, xshift=2cm] {Process 2b};
\node (out1) [io, below of=pro2a] {Output};
\node (stop) [startstop, below of=out1] {Stop};

\draw [arrow] (start) -- (in1);
\draw [arrow] (in1) -- (pro1);
\draw [arrow] (pro1) -- (dec1);
\draw [arrow] (dec1) -- node[anchor=east] {yes} (pro2a);
\draw [arrow] (dec1) -- node[anchor=south] {no} (pro2b);
\draw [arrow] (pro2b) |- (pro1);
\draw [arrow] (pro2a) -- (out1);
\draw [arrow] (out1) -- (stop);

\end{tikzpicture}

```




```
$$

\begin{split}
\mathrm{Var}(\hat{\beta}) & =\mathrm{Var}((X'X)^{-1}X'y)\\
 & =(X'X)^{-1}X'\mathrm{Var}(y)((X'X)^{-1}X')'\\
 & =(X'X)^{-1}X'\mathrm{Var}(y)X(X'X)^{-1}\\
 & =(X'X)^{-1}X'\sigma^{2}IX(X'X)^{-1}\\
 & =(X'X)^{-1}\sigma^{2}
\end{split}

$$
```



\begin{align} 
g(X_{n}) &= g(\theta)+g'({\tilde{\theta}})(X_{n}-\theta) \notag \\
\sqrt{n}[g(X_{n})-g(\theta)] &= g'\left({\tilde{\theta}}\right)
  \sqrt{n}[X_{n}-\theta ] (\#eq:align)
\end{align} 




```{theorem, name="Pythagorean theorem"}
For a right triangle, if $c$ denotes the length of the hypotenuse
and $a$ and $b$ denote the lengths of the other two sides, we have
$$a^2 + b^2 = c^2$$
```


